# Part2.1-Model

$\theta:$

the Net Present Value of Stream of benefits

+ If she decides to reject the technology, she receives nothing and no longer gathers information about the technology.

+ If she decides to *adopt* the technology, she pays a fixed adoption cost K and receives a net expected benefit:

$$\int_{\theta} \theta \pi(\theta)d\theta - K$$

$\theta$ has the density $\pi$.


+ Now, if consumer choose to gather additional information, she pays *c* *in that period* and observe the signal x, drawn with likelihood function 

$$L(x|\theta)$$

Having observed signal x, the consumer then updates her prior $\pi$ using Baye's rule:

$$\prod(\theta;\pi,x) = $$






You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(methods).

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].
change new line